\documentclass{article}

\usepackage[textwidth=7in,textheight=10in]{geometry}
\usepackage{graphicx}
\usepackage{/Users/eleanorbrush/Documents/custom2}
\usepackage{wasysym}
\usepackage{color}
\usepackage[numbers,sort&compress]{natbib}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
%% for inline R code: if the inline code is not correctly parsed, you will see a message
\newcommand{\x}[1]{\text{#1}}
\newcommand{\Cov}{\text{Cov}}
\usepackage{lscape} 
\begin{document}

\section{Introduction}
\begin{itemize}
\item ``Because two-locus and other types of model cannot describe inheritance and selection for continuously varying traits (such as ornaments and preferences), these models are fundamentally disconnected from the empirical study of sexual selection," \cite{Mead:2004uq}

\item ``The male traits most likely to become exaggerated by such mechanisms are those under weak natural selection and subject to relatively large variance in female sexual preferences, such as some behavioral and morphological elements of courtship and mating," \cite{Lande:1981fk}

\item quantitative genetics model / like mine: ``Variation among females in their preferences selects for increased variance in the male trait; we assume that this effect is weak by requiring that $\sigma_\x{z}^2\sigma_\x{y}^2<<1$," \cite{Kirkpatrick:1990kx} WHY?!?!

\item two-allele model: ``Neither copying model supports variation at the male trait locus, and copying makes it more difficult for a novel male trait phenotype to spread," \cite{Kirkpatrick:1994vn}. ``Since Lill's study, anecdotal evidence for copying has also been found in other species of birds, mammals, and fishes (reviewed by Gibson and Hoglund 1992; Pruett-Jones 1992)," \cite{Kirkpatrick:1994vn}. ``Bradbury and Gibson (1983) and Bradbury et al. (1985) found that the large variance of male mating success observed in sage grouse could not be plausibly attributed to independent female choice, and suggested that copying might be responsible," \cite{Kirkpatrick:1994vn}. ``Y-linkage is of interest because many of the loci that affect sexually-selected male coloration in guppies are Y-linked (Winge 1927; Haskins et al. 1961)," \cite{Kirkpatrick:1994vn}. ``Copying itself does not support polymorphism in the male trait, at least in haploid and Y-linked systems," \cite{Kirkpatrick:1994vn}. ``Guppies are a perplexing example in this context. The species is famous for highly polymorphic male coloration (Endler 1983) which is known to be under sexual selection (Endler 1980, 1983; Breden and Stoner 1987; Houde 1987, 1988; Stoner and Breden 1988; Houde and Endler 1990) and is at least in part caused by Y-linked loci (Winge 1927; Haskins et al 1961)," \cite{Kirkpatrick:1994vn}.

\item ``Mate preferences can be genetically determined (Saether et al. 2007), but they can also be learned (Virzijden et al. 2012). For example, in sticklebacks females learn to prefer mates with phenotypes similar to their fathers (Kozak et al. 2011) and in some cichlids females learn to prefer mates with phenotypes similar to their mothers (Verzijden et al. 2008). Recent work suggests that learned preferences for parental phenotypes can promote speciation (Verzijden et al. 2005; Servedio and Dukas 2013)," \cite{Gilman:2015fk}.
\end{itemize}

\section{Question}
\begin{enumerate}
\item H1 Song learning can decelerate speciation by allowing for genetically diverse birds to mate with each other, maintaining gene flow between subpopulations that might either begin to diverge
\item H2 Song learning can accelerate speciation by increasing standing genetic variation, which would allow for quicker divergence once new selection pressures arise \cite{Lachlan:2004tg}
\item H3 Song learning can accelerate speciation because culturally inherited traits can evolve more quickly than genetically inherited ones \cite{Irwin:2012hc}
\end{enumerate}

\begin{table}
\caption{\label{summmary_previous} Summary of choices made in previous models}
\ra{1.3}
\begin{tabular}{@{}l@{}llllll}
&\citet{Lachlan:2004tg}
\\ \male trait(s) & allele A  / a: song predisposition
 \\ & song
\\ How \male\ trait is learned 
\\ Inherited 
\\\female\ trait(s) 
\\How \female\ trait is learned 
\\Inherited
\\ Errors
\\ Population structure
\\ Mating structure
\\ \female\ preference
\\ Selection
\end{tabular}
\end{table}

\section{Goals}

\section{Model}

\subsection{Continuous traits }

Each male has a song and each female has preference for a particular song. She will mate with males with songs other than her preferred song, but the probability of her doing so decreases as the potential mate's song gets less similar to her preferred song. Each female mates once and chooses a male according to her preferences and the distribution of songs present in the population. Each male, therefore, may breed multiple times or not at all. We assume that generations are non-overlapping, so once the adults breed they die and we can shift our focus to the new generation. To begin with, we assume that males acquire their songs from their fathers at birth and females acquire their preferences from their mothers at birth. We further assume an unbiased sex ratio. Before the new generation mates, each male has a small probability of ``mutating" its song. This can be interpreted as a learning error or as innovation. After mutation, the new males and females mate. 

Mathematically, each male has a song $x\in \R$ and each female has a preference $y\in\R$. The probability density of the male songs will be written $P_\text{m}(x)$ and the probability density of female preferences will be written $P_\text{f}(y)$. The preference of a female with preference $y$ mates for a male with song $x$ is 
\begin{equation*}
f_y(x)=\frac{1}{\sqrt{2 \pi \sigma^2}}\exp\left(-\frac{(x-y)^2}{2\sigma^2}\right),
\end{equation*}
which is maximal when $x=y$ and decreases as $|x-y|$ increases. The probability that a female with preference $y$ choose a male with song $x$ is 
\begin{equation*}
\frac{P_\text{m}(x)f_y(x)}{\int_\R P_\text{m}(x')f_y(x')dx'},
\end{equation*}
so the probability of a $(x,y)$ pair mating is then
\begin{equation*}
P_\text{mate}(x,y)=\frac{P_\text{f}(y)P_\text{m}(x)f_y(x)}{\int_\R P_\text{m}(x')f_y(x')dx'}=\frac{P_\text{f}(y)P_\text{m}(x)f_y(x)}{Z_y},
\end{equation*}
where $Z_y$ is the normalizing factor $\int_\R P_\text{m}(x')f_y(x')dx'$.
Each such pair will produce a male with song $x$ and a female with preference $y$. Before mating, the male's song changes to $x-\delta_\text{mut}$ with probability $p_\text{mut}/2$ and to $x+\delta_\text{mut}$ with probability $p_\text{mut}/2$. Under these assumptions, the probability density of female preferences does not change over time:
\begin{equation*}
P_\text{f}(y,t+1)=P_\text{f}(y,t).
\end{equation*}
The probability density of male songs in the next generation, before mutating and after mutating, follows
\begin{align*}
P_\text{m}(x,t+1/2)&=\int_\R P_\text{mate}(x,y,t) dy
\\P_\text{m}(x,t+1)&=(1-p_\text{mut})P_\text{m}(x,t+1/2)+p_\text{mut}/2P_\text{m}(x-\delta_\text{mut},t+1/2)+p_\text{mut}/2P_\text{m}(x+\delta_\text{mut},t+1/2)
\end{align*}
 (Population dynamics are modeled in Code \ref{dynamics}. Global and / or needed parameters are given in Code \ref{parameters}.)

We start with mixtures of normal distributions of both male and female:
\begin{align*}
P_\text{f}(y,0)&=p_\text{f}\frac{1}{\sqrt{2\pi\sigma_\text{f}^2}}\exp\left(-\frac{(y+1)^2}{2\sigma_\text{f}^2}\right)+(1-p_\text{f})\frac{1}{\sqrt{2\pi\sigma_\text{f}^2}}\exp\left(-\frac{(y-1)^2}{2\sigma_\text{f}^2}\right)
\\P_\text{m}(x,0)&=p_\text{m}\frac{1}{\sqrt{2\pi\sigma_\text{m}^2}}\exp\left(-\frac{(x+1)^2}{2\sigma_\text{m}^2}\right)+(1-p_\text{m})\frac{1}{\sqrt{2\pi\sigma_\text{m}^2}}\exp\left(-\frac{(x-1)^2}{2\sigma_\text{m}^2}\right)
\end{align*}
Even with a continuous distribution of female preferences, we find that after several generations, the male song distribution is concentrated in several discrete peaks (Figure \ref{fig:plot_peaks}). (Parameters and initial conditions given in Code \ref{peaks}.)

There are three critical parameters:
\begin{table}
\caption{\label{parameters} Parameters}
\ra{1.3}
\begin{tabular}{llllll}
$\sigma^2$ & width of female preference function
\\$\sigma_\text{f}^2$ & variance of female preferences within each population
\\$\sigma_\text{m}^2$ & variance of male traits within each population
\end{tabular}
\end{table}

Mutations give rise to a small number of males with song traits that are slightly higher (lower) than the rest of the population. The ``edge" females that most prefer these extreme songs have limited options because they do not like the songs most males are singing. They therefore mate with the new ``edge" males with very high probability, which leads to a very fast increase of these songs. As mutations continue to generate new songs, extreme songs will be selected for at the expense of similar songs closer to the middle of the song range. Ultimately, this results in a number of discrete songs at high density.

Ignoring mutations for the moment, the rate of change of the probability density of a particular song is given by 
\begin{equation}
\frac{P_\text{m}(x,t+1)}{P_\text{m}(x,t)}= \int _\R\frac{ P_\text{f}(y)f_y(x)}{Z_y}dy \label{growth}
\end{equation}
This shows that the normalizing factor $Z_y$ affects how the density of male songs changes from one generation to the next: if a male is recognized by females with very few options (small $Z_y$), then the density of that song will increase more than the song a male recognized by females with many options (large $Z_y$) (Figure \ref{fig:explanation_plot}).

\subsection{Analysis} 
\begin{claim} \label{norm_prod} $\exp\left(-\frac{(x-\mu_\text{a})^2}{2\sigma_\text{a}^2}\right)\times \exp\left(-\frac{(x-\mu_\text{b})^2}{2\sigma_\text{b}^2}\right)=\exp\left(-\frac{(x-\mu_\text{ab})^2}{2\sigma_\text{ab}^2}\right)\times\exp\left(-\frac{(\mu_\text{a}-\mu_\text{b})^2}{2(\sigma_\text{a}^2+\sigma_\text{b}^2)}\right)$ where $\mu_\text{ab}=\frac{\mu_\text{a}\sigma_\text{b}^2+\mu_\text{b}\sigma_\text{a}^2}{\sigma_\text{a}^2+\sigma_b^2}$ and $\sigma_\text{ab}^2=\frac{\sigma_\text{a}^2\sigma_\text{b}^2}{\sigma_\text{a}^2+\sigma_\text{b}^2}$
\end{claim}

\begin{landscape}

\begin{align*}
P_\x{m}(x,y) & \sim N\left(\mu_\x{m},\Sigma_\x{m}\right) \text{ where } \ \ \mu_\x{m} = \left(\begin{array}{cc} \mu_{\x{m}x} \\ \mu_{\x{m}y}  \end{array}\right) \ \ \Sigma_\x{m} = \left(\begin{array}{cccc}\sigma_{\x{m}x}^2 & \rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} \\  \rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} & \sigma_{\x{m}y}^2\end{array}\right)
\\f_y(x)  & \sim N\left(y,\sigma^2\right)
\\ \Rightarrow P_\x{m}(x_1,y_1)f_{y_2}(x_1) & = \frac{1}{2\pi\sqrt{|\bar{\Sigma}_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_m-\bar{\mu}_\x{m})^T\bar{\Sigma}_{\x{m}}^{-1}(\vec{x}_\x{m}-\bar{\mu}_\x{m})\right)\frac{1}{\sqrt{2\pi(\sigma^2+\sigma_{\x{m}x}^2)}}\exp\left(-\frac{(y_2-\mu_{\x{m}x})^2}{2(\sigma^2+\sigma_{\x{m}x}^2)}\right)
\\ \text{ where } \bar{\mu}_\x{m}&=\left(\begin{array}{cc}\frac{\sigma^2\mu_{\x{m}x}}{\sigma^2+\sigma_{\x{m}x}^2}+\frac{\sigma_{\x{m}x}^2y_2}{\sigma^2+\sigma_{\x{m}x}^2} \\ \mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}}{\sigma^2+\sigma_{\x{m}x}^2}(y_2-\mu_{\x{m}x})\end{array}\right)=\left(\begin{array}{cc}\frac{\sigma^2\mu_{\x{m}x}}{\sigma^2+\sigma_{\x{m}x}^2}+\frac{\sigma_{\x{m}x}^2y_2}{\sigma^2+\sigma_{\x{m}x}^2} \\ \mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}(y_2-\mu_{\x{m}x})\end{array}\right) 
\\\text{ and } \bar{\Sigma}_\x{m}&=\left(\begin{array}{cccc}\frac{\sigma^2\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2} & \frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2} \\ \frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2} & \left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}+\frac{\sigma_{\x{m}x}^2(1-\rho_\x{m}^2)}{\sigma^2+\sigma_{\x{m}x}^2}\right)\sigma_{\x{m}y}^2 \end{array}\right)=\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\Sigma_{\x{m}}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\begin{array}{cc}0 & 0 \\ 0 & (1-\rho_\x{m}^2)\sigma_{\x{m}y}^2 \end{array}\right)
\\ \Rightarrow \int\int P_\x{m}(x_1,y_1)f_{y_2}(x_1)dx_1dy_1 &= \frac{1}{\sqrt{2\pi(\sigma^2+\sigma_{\x{m}x}^2)}}\exp\left(-\frac{(y_2-\mu_{\x{m}x})^2}{2(\sigma^2+\sigma_{\x{m}x}^2)}\right)
\\ \Rightarrow \frac{P_\x{m}(x_1,y_1)f_{y_2}(x_1)}{\int\int P_\x{m}(x_1,y_1)f_{y_2}(x_1)dx_1dy_1} &=\frac{1}{2\pi\sqrt{|\bar{\Sigma}_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_m-\bar{\mu}_\x{m})^T\bar{\Sigma}_{\x{m}}^{-1}(\vec{x}_\x{m}-\bar{\mu}_\x{m})\right)
\\ \Rightarrow \frac{P_\x{f}(x_2,y_2)P_\x{m}(x_1,y_1)f_{y_2}(x_1)}{\int\int P_\x{m}(x_1,y_1)f_{y_2}(x_1)dx_1dy_1} &=\frac{1}{2\pi\sqrt{|\Sigma_\x{f}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\mu_\x{f})^T\Sigma_\x{f}^{-1}(\vec{x}_\x{f}-\mu_\x{f})\right)\frac{1}{2\pi\sqrt{|\bar{\Sigma}_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_m-\bar{\mu}_\x{m})^T\bar{\Sigma}_{\x{m}}^{-1}(\vec{x}_\x{m}-\bar{\mu}_\x{m})\right) 
\\&\text{ CAN INTEGRATE } x_1,y_1,x_2
\end{align*}
\begin{align*}
\\\text{ OR } \frac{P_\x{m}(x_1,y_1)f_{y_2}(x_1)}{\int\int P_\x{m}(x_1,y_1)f_{y_2}(x_1)dx_1dy_1} & = \frac{P_\x{m}(x_1,y_1)f_{y_2}(x_1)}{\frac{1}{\sqrt{2\pi(\sigma^2+\sigma_{\x{m}x}^2)}}\exp\left(-\frac{(y_2-\mu_{\x{m}x})^2}{2(\sigma^2+\sigma_{\x{m}x}^2)}\right)}
\\&=P_\x{m}(x_1,y_1)\frac{\sqrt{\sigma^2+\sigma_{\x{m}x}^2}}{\sqrt{\sigma^2}}\exp\left(-\frac{(y_2-x_1)^2}{2\sigma^2}\right)\exp\left(-\frac{(y_2-\mu_{\x{m}x})^2}{2(-\sigma^2-\sigma_{\x{m}x}^2)}\right)
\\&=P_\x{m}(x_1,y_1)\frac{\sqrt{\sigma^2+\sigma_{\x{m}x}^2}}{\sqrt{\sigma^2}}\exp\left(-\frac{\left(y_2-\left(\frac{(-\sigma^2-\sigma_{\x{m}x}^2)x_1+\mu_{\x{m}x}\sigma^2}{-\sigma_{\x{m}x}^2}\right)\right)^2}{2\frac{\sigma^2(-\sigma^2-\sigma_{\x{m}x}^2)}{-\sigma_{\x{m}x}^2}}\right)\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2(-\sigma_{\x{m}x}^2)}\right)
\\&=\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\frac{\sqrt{\sigma^2+\sigma_{\x{m}x}^2}}{\sqrt{\sigma^2}}\exp\left(-\frac{\left(y_2-\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma_{\x{m}x}^2}}\right)
\\ \Rightarrow \frac{P_\x{f}(x_2,y_2)P_\x{m}(x_1,y_1)f_{y_2}(x_1)}{\int\int P_\x{m}(x_1,y_1)f_{y_2}(x_1)dx_1dy_1} &=\frac{1}{2\pi\sqrt{|\Sigma_\x{f}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\mu_\x{f})^T\Sigma_\x{f}^{-1}(\vec{x}_\x{f}-\mu_\x{f})\right)\exp\left(-\frac{\left(y_2-\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma_{\x{m}x}^2}}\right)\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\frac{\sqrt{\sigma^2+\sigma_{\x{m}x}^2}}{\sqrt{\sigma^2}}
\\ &=\frac{1}{2\pi\sqrt{|\Sigma_{\x{f}}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\exp\left(-\frac{\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}{\sigma_{\x{m}x}^2}}\right)\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\frac{\sqrt{\sigma^2+\sigma_{\x{m}x}^2}}{\sqrt{\sigma^2}}
\\ \text{ where } \bar{\mu}_\x{f}&=\left(\begin{array}{cc}\mu_{\x{f}x}+\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)\\ \frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\mu_{\x{f}y}+\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2} \end{array}\right)
\\ \text{ and } \bar{\Sigma}_{f}&=\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\Sigma_{\x{f}}+\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\left(\begin{array}{cc}(1-\rho_\x{f}^2)\sigma_{\x{f}x}^2 & 0 \\ 0 & 0 \end{array}\right)
\\ |\bar{\Sigma}_\x{f}|&=|\Sigma_\x{f}|\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}
\\\Rightarrow \frac{P_\x{f}(x_2,y_2)P_\x{m}(x_1,y_1)f_{y_2}(x_1)}{\int\int P_\x{m}(x_1,y_1)f_{y_2}(x_1)dx_1dy_1}&=\frac{1}{2\pi\sqrt{|\Sigma_{\x{f}}|\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\exp\left(-\frac{\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}{\sigma_{\x{m}x}^2}}\right)\times 
\\&\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\sqrt{\frac{\sigma^2+\sigma_{\x{m}x}^2}{\sigma^2}}\sqrt{\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}
\\&=\frac{1}{2\pi\sqrt{|\bar{\Sigma}_{\x{f}}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\exp\left(-\frac{\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}{\sigma_{\x{m}x}^2}}\right)\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\sqrt{\frac{(\sigma^2+\sigma_{\x{m}x}^2)^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}
\\&=\frac{1}{2\pi\sqrt{|\bar{\Sigma}_{\x{f}}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\sqrt{\frac{(\sigma^2+\sigma_{\x{m}x}^2)^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}} 
\\&\text{ CAN INTEGRATE } y_1,x_2,y_2
\end{align*}

\begin{align*}
\\P_\text{mate}(x_1,y_1,x_2,y_2)&=\frac{1}{2\pi\sqrt{|\bar{\Sigma}_{\x{f}}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\sqrt{\frac{(\sigma^2+\sigma_{\x{m}x}^2)^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}} 
\\ \Rightarrow \int P_\text{mate}dy_1&=\frac{1}{2\pi\sqrt{|\bar{\Sigma}_{\x{f}}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\frac{\frac{1}{\sqrt{2\pi\sigma_{\x{m}x}^2}}\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\sqrt{\frac{(\sigma^2+\sigma_{\x{m}x}^2)^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}} 
\\&=\frac{1}{2\pi\sqrt{|\bar{\Sigma}_{\x{f}}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\frac{1}{\sqrt{2\pi\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}}\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)
\\ \Rightarrow \int\int P_\text{mate}dy_1dy_2&=\frac{1}{\sqrt{2\pi\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2(1-\rho_\x{f}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}}\exp\left(-\frac{\left(x_2-\mu_{\x{f}x}-\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)\right)^2}{2\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2(1-\rho_\x{f}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}\right)\times
\\&\frac{1}{\sqrt{2\pi\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}}\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)
\\ \Rightarrow \int\int P_\text{mate}dy_1dy_2&=\frac{1}{\sqrt{2\pi\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2(1-\rho_\x{f}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}}\exp\left(-\frac{\left(x_2-\mu_{\x{f}x}-\sigma_{\x{f}x}\frac{\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma^2+\sigma_{\x{m}x}^2}{\sigma_{\x{m}x}\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\left(x_1-\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)\right)^2}{2\left(1-\frac{\rho_\x{f}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}\right)\times 
\\ &\frac{1}{\sqrt{2\pi\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}}\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)
\end{align*}


\begin{align*}
\Rightarrow P_\text{mate}(x_1,x_2)&\sim N\left(\left(\begin{array}{cc}\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y} \\ \mu_{\x{f}x} \end{array}\right),\left(\begin{array}{cc} \sigma_{\x{m}x}'^2 & \rho_{x_1,x_2}\sigma_{\x{m}x}'\sigma_{\x{f}x}' \\ \rho_{x_1,x_2}\sigma_{\x{m}x}'\sigma_{\x{f}x}' & \sigma_{\x{f}x}'^2  \end{array}\right)\right)
\\ \text{ where } \sigma_{\x{m}x}'^2&=\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}
\\ \text{ and } \sigma_{\x{f}x}'^2&=\sigma_{\x{f}x}^2 
\\ \text{ and } \rho_{x_1,x_2} &= \frac{\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}
\end{align*}

{\tiny 
\begin{align*}
\int P_\text{mate}(x_1,y_1,x_2,y_2)dy_1 &= \frac{1}{2\pi\sqrt{|\bar{\Sigma}_{\x{f}}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\bar{\mu}_{\x{f}})^T\bar{\Sigma}_\x{f}^{-1}(\vec{x}_\x{f}-\bar{\mu}_\x{f})\right)\frac{1}{\sqrt{2\pi\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}}\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)&
\\ \Rightarrow \int \int P_\text{mate}(x_1,y_1,x_2,y_2)dy_1dx_2 &=\frac{1}{\sqrt{2\pi\sigma_{\x{f}y}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}}\exp\left(-\frac{\left(y_2-\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x})}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\mu_{\x{f}y}+\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)\right)^2}{2\sigma_{\x{f}y}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\right)\times
\\&\frac{1}{\sqrt{2\pi\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}}\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)
\\&=\frac{1}{\sqrt{2\pi\sigma_{\x{f}y}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}}\exp\left(-\frac{\left(y_2-\left(\mu_{\x{f}y}+\frac{\sigma_{\x{f}y}^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2\mu_{\x{f}y}}{\sigma^2+\sigma_{\x{m}x}^2}\right)\right)\right)^2}{2\sigma_{\x{f}y}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\right)\times
\\&\frac{1}{\sqrt{2\pi\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}}\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)
\\ \Rightarrow P_\text{mate}(x_1,y_2)&\sim N\left(\left(\begin{array}{cc}\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y} \\ \mu_{\x{f}y} \end{array}\right),\left(\begin{array}{cc} \sigma_{\x{m}x}'^2 & \rho_{x_1,y_2}\sigma_{\x{m}x}'\sigma_{\x{f}y}' \\ \rho_{x_1,y_2}\sigma_{\x{m}x}'\sigma_{\x{f}y}' & \sigma_{\x{f}y}'^2  \end{array}\right)\right)
\\ \text{ where } \sigma_{\x{m}x}'^2&=\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}
\\ \text{ and } \sigma_{\x{f}y}'^2&=\sigma_{\x{f}y}^2
\\ \text{ and } \rho_{x_1,y_2}&=\frac{\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}
\end{align*}
}
\begin{align*}
\int\int P_\text{mate}(x_1,y_1,x_2,y_2)dx_2dy_2&=\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\sqrt{\frac{(\sigma^2+\sigma_{\x{m}x}^2)^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}} 
\\&=\frac{1}{\sqrt{2\pi(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}}\frac{1}{\sqrt{2\pi\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}} \exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\times
\\&\exp\left(-\frac{\left(y_1-\left(\mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}(x_1-\mu_{\x{m}x}\right)\right)^2}{2(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}\right)
\\&=\frac{1}{\sqrt{2\pi\sigma_{\x{m}x}'^2}}\exp\left(-\frac{(x_1-\mu_{\x{m}x}')^2}{2\sigma_{\x{m}x}'^2}\right)\times
\\&\frac{1}{\sqrt{2\pi(1-\rho_{x_1,y_2}^2)\sigma_{\x{m}y}'^2}}\exp\left(-\frac{(y_1-(\mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}(\mu_{\x{m}x}'-\mu_{\x{m}x})+\frac{\rho_{x_1,y_1}\sigma_{\x{m}y}'}{\sigma_{\x{m}x}'}(x_1-\mu_{\x{m}x}')))^2}{2(1-\rho_{x_1,y_1}^2)\sigma_{\x{m}y}'^2}\right)
\\ \text{ where } \rho_{x_1,y_1}&=\rho_\x{m}\sqrt{\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}}
\\&=\frac{1}{\sqrt{2\pi\sigma_{\x{m}x}'^2}}\exp\left(-\frac{(x_1-\mu_{\x{m}x}')^2}{2\sigma_{\x{m}x}'^2}\right)\frac{1}{\sqrt{2\pi(1-\rho_{x_1,y_2}^2)\sigma_{\x{m}y}'^2}}\exp\left(-\frac{(y_1-(\mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\mu_{\x{f}y}-\mu_{\x{m}x}\right)+\frac{\rho_{x_1,y_1}\sigma_{\x{m}y}'}{\sigma_{\x{m}x}'}(x_1-\mu_{\x{m}x}')))^2}{2(1-\rho_{x_1,y_2}^2)\sigma_{\x{m}y}'^2}\right)
\\ \Rightarrow P_\text{mate}(x_1,y_1)&\sim N\left(\left(\begin{array}{cc}\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y} \\  \mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}(\mu_{\x{f}y}-\mu_{\x{m}x})\end{array}\right),\left(\begin{array}{cc}\sigma_{\x{m}x}'^2 & \rho_{x_1,y_1}\sigma_{\x{m}x}'\sigma_{\x{m}y}' \\\rho_{x_1,y_1}\sigma_{\x{m}x}'\sigma_{\x{m}y}'& \sigma_{\x{m}y}'^2 \end{array}\right)\right)
\end{align*}

\begin{align*}
\int P_\text{mate}(x_1,y_1,x_2,y_2)dy_2&= \frac{1}{\sqrt{2\pi \left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}}\exp\left(-\frac{\left(x_2-\left(\mu_{\x{f}x}+\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)\right)\right)^2}{2 \left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}\right)\times 
\\ &\exp\left(-\frac{\left(x_1-\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\frac{P_\x{m}(x_1,y_1)}{\exp\left(-\frac{(x_1-\mu_{\x{m}x})^2}{2\sigma_{\x{m}x}^2}\right)}\sqrt{\frac{(\sigma^2+\sigma_{\x{m}x}^2)^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}} 
\\&=\frac{1}{\sqrt{2\pi \left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}} \exp\left(-\frac{\left(x_2-\left(\mu_{\x{f}x}+\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)\right)\right)^2}{2 \left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}\right)\times 
\\&\frac{1}{2\pi\sqrt{\sigma_{\x{m}x}'^2}}\exp\left(-\frac{\left(x_1-\left(\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\frac{1}{\sqrt{2\pi(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}}\exp\left(-\frac{\left(y_1-\mu_{\x{m}y}-\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}(x_1-\mu_{\x{m}x})\right)^2}{2(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}\right)
\\&=\frac{1}{\sqrt{2\pi \left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}} \exp\left(-\frac{\left(x_2-\left(\mu_{\x{f}x}+\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}\frac{\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)\right)\right)^2}{2 \left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}x}^2}\right)\times 
\\&\frac{1}{\sqrt{2\pi\sigma_{\x{m}x}'^2}} \exp\left(-\frac{\left(x_1-\left(\frac{\mu_{\x{m}x}\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)\right)^2}{2\frac{\sigma_{\x{m}x}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\frac{1}{2\pi\sqrt{(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}}\exp\left(-\frac{(x_1-(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})))^2}{2\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2}\right)\exp\left(-\frac{(y_1-\mu_{\x{m}y})^2}{2\sigma_{\x{m}y}^2}\right)
\\&=\frac{1}{2\pi\sqrt{|\Sigma_{x_1,x_2}|}}\exp\left(-(v-\mu_{x_1,x_2})^T\Sigma_{x_1,x_2}^{-1}(v-\mu_{x_1,x_2})\right)\times
\\&\frac{1}{\sqrt{2\pi(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}}\exp\left(-\frac{(x_1-(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})))^2}{2\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2}\right)
\\ \text{ where }  v&=(x_1,x_2)^T, \ \mu_{x_1,x_2}=\left(\begin{array}{cc}\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y} \\ \mu_{\x{f}x} \end{array}\right)
\\ \text{ and  } \Sigma_{x_1,x_2} &= \left(\begin{array}{cc}\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}\sigma_{\x{m}x}^2 & \frac{\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma_{\x{m}x}\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{f}y} \\ \frac{\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma_{\x{m}x}\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{f}y} & \sigma_{\x{f}x}^2 \end{array}\right)
\\&=\frac{1}{2\pi\sqrt{|\Sigma_{x_1,x_2}|}}\exp\left(-(v-\nu)^TM^{-1}(v-\nu)\right)\frac{1}{\sqrt{2\pi(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}}\exp\left(-\frac{\left(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})-\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)\right)^2}{2\left(\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}+\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)\sigma_{\x{m}x}^2}\right)
\end{align*}

\begin{align*}
\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}\sigma_{\x{m}x}^2+\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2&=\sigma_{\x{m}x}^2\left(\frac{\rho_\x{m}^2(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2)+(\sigma^2+\sigma_{\x{m}x}^2)^2(1-\rho_\x{m}^2)}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2} \right)
\\&=\sigma_{\x{m}x}^2\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)
\\&=\frac{\sigma_{\x{m}x}^2\sigma_{\x{m}y}'^2}{\sigma_{\x{m}y}^2\rho_\x{m}^2}
\\ \Rightarrow \nu&=\left(\begin{array}{cc}\frac{\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)\left(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})\right)+\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)}{\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}} \\ \mu_{\x{f}x}+\frac{\rho_{x_1,x_2}\sigma_{\x{m}x}'\sigma_{\x{f}x}}{\sigma_{\x{m}x}^2\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)}\left(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})-\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)\right) \end{array}\right)
\\&=\left(\begin{array}{cc}\frac{\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)\left(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})\right)+\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)}{\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}} \\ \mu_{\x{f}x}+\frac{\rho_{x_1,x_2}\sigma_{\x{m}x}'\sigma_{\x{f}x}}{\sigma_{\x{m}x}^2\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)}\left(\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\mu_{\x{f}y}-\mu_{\x{m}x}\right)\right) \end{array}\right)
\\&=\left(\begin{array}{cc}\frac{\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)\left(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})\right)+\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)}{\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}} \\ \mu_{\x{f}x}+\frac{\rho_{x_1,x_2}\sigma_{\x{m}x}'\sigma_{\x{f}x}\sigma_{\x{m}x}}{\rho_\x{m}\sigma_{\x{m}y}\sigma_{\x{m}x}^2\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)}\left(y_1-\mu_{\x{m}y}-\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\mu_{\x{f}y}-\mu_{\x{m}x}\right)\right) \end{array}\right)
\\&=\left(\begin{array}{cc}\frac{\left(\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)\left(\mu_{\x{m}x}+\frac{1}{\rho_\x{m}}\frac{\sigma_{\x{m}x}}{\sigma_{\x{m}y}}(y_1-\mu_{\x{m}y})\right)+\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}\right)}{\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}} \\ \mu_{\x{f}x}+\frac{\rho_{x_1,x_2}\sigma_{\x{m}x}'\sigma_{\x{f}x}}{\sigma_{\x{m}y}\sigma_{\x{m}x}\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}(\sigma^2+\sigma_{\x{m}x}^2)^2}\right)}\left(y_1-\mu_{\x{m}y}-\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\mu_{\x{f}y}-\mu_{\x{m}x}\right)\right) \end{array}\right)
\\ \rho_{x_1,x_2}\sigma_{\x{m}x}'&=\frac{\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{m}x}=\frac{\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}
\\ \Rightarrow \nu_2&= \mu_{\x{f}x}+\sigma_{\x{f}x}\frac{\rho_\x{m}\rho_\x{f}\sigma_{\x{m}x}}{\sigma_{\x{m}y}\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\right)}\left(y_1-\mu_{\x{m}y}-\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\mu_{\x{f}y}-\mu_{\x{m}x}\right)\right)
\\&= \mu_{\x{f}x}+\frac{\sigma_{\x{f}x}\rho_\x{m}\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sigma_{\x{m}y}'\sqrt{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\left(y_1-\mu_{\x{m}y}'\right)
\\&=\mu_{\x{f}x}+\frac{\rho_{y_1,x_2}\sigma_{\x{f}x}}{\sigma_{\x{m}y}'}(y_1-\mu_{\x{m}y}')
\\ \text{ where } \rho_{y_1,x_2}&=\frac{\rho_\x{m}\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}
\end{align*}
\begin{align*}
\text{ and } M&=\frac{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2}{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2}\Sigma_{x_1,x_2}+\left(\begin{array}{cc}0 & 0 \\ 0 & \frac{(1-\rho_{x_1,x_2}^2)\sigma_{\x{m}x}'^2\sigma_{\x{f}y}^2}{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2} \end{array}\right)
\\&=\frac{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2}{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2}\Sigma_{x_1,x_2}+\left(\begin{array}{cc}0 & 0 \\ 0 & \frac{|\Sigma_{x_1,x_2}|}{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2} \end{array}\right)
\\ \Rightarrow |M| &=\left(\frac{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2}{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2}\right)^2|\Sigma_{x_1,x_2}|+\frac{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2\sigma_{\x{m}x}'^2}{\left(\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2\right)^2}|\Sigma_{x_1,x_2}|
\\&=\frac{\left(\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2\right)\left(\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2\right)}{\left(\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2\right)^2}|\Sigma_{x_1,x_2}|
\\&=\frac{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2}{\frac{1-\rho_\x{m}^2}{\rho_\x{m}^2}\sigma_{\x{m}x}^2+\sigma_{\x{m}x}'^2}|\Sigma_{x_1,x_2}|
\\&=\frac{(1-\rho_\x{m}^2)(\sigma^2+\sigma_{\x{m}x}^2)^2}{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}|\Sigma_{x_1,x_2}|
\\&=\frac{(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}{\sigma_{\x{m}y}'^2}|\Sigma_{x_1,x_2}|
\\\text{ and } \Rightarrow M_{2,2}&=\left(1-\frac{\sigma_{\x{m}x}'^2\rho_{x_1,x_2}^2}{\sigma_{\x{m}x}^2\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\rho_\x{m}^2(\sigma^2+\sigma_{\x{m}x}^2)^2}}\right)\sigma_{\x{f}y}^2
\\&=\left(1-\frac{\rho_\x{f}^2\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}\right)\sigma_{\x{f}y}^2
\\&=\left(1-\rho_{y_1,x_2}^2\right)\sigma_{\x{f}y}^2
\end{align*}

\begin{align*}
\Rightarrow \int P_\text{mate} y_2&=\frac{1}{2\pi\sqrt{|M|\left(\frac{\sigma_{\x{m}y}'^2}{(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}\right)}}\exp\left(-(v-\nu)^TM^{-1}(v-\nu)\right)\frac{1}{\sqrt{2\pi(1-\rho_\x{m}^2)\sigma_{\x{m}y}^2}}\exp\left(-\frac{(y_1-\mu_{\x{m}y}')^2}{2\frac{\rho_\x{m}^2\sigma_{\x{m}y}^2}{\sigma_{\x{m}x}^2}\frac{\sigma_{\x{m}x}^2\sigma_{\x{m}y}'^2}{\sigma_{\x{m}y}^2\rho_\x{m}^2}}\right)
\\ \Rightarrow \int P_\text{mate} dx_1dy_2 &= \frac{1}{\sqrt{2\pi (1-\rho_{y_1,x_2}^2)\sigma_{\x{f}y}^2}}\exp\left(-\frac{\left(x_2-\mu_{\x{f}x}-\frac{\rho_{y_1,x_2}\sigma_{\x{f}x}}{\sigma_{\x{m}y}'}(y_1-\mu_{\x{m}y}')\right)^2}{2(1-\rho_{y_2,x_1}^2)\sigma_{\x{f}y}^2}\right)\frac{1}{\sqrt{2\pi\sigma_{\x{m}y}'^2}}\exp\left(-\frac{(y_1-\mu_{\x{m}y}')^2}{2\sigma_{\x{m}y}'^2}\right)
\\ \Rightarrow \int P_\text{mate} dx_1dy_2&\sim N\left(\left(\begin{array}{cc} \mu_{\x{m}y}' \\ \mu_{\x{f}x}\end{array} \right),\left(\begin{array}{cc} \sigma_{\x{m}y}'^2 & \rho_{y_1,x_2}\sigma_{\x{m}y}'\sigma_{\x{f}x} \\ \rho_{y_1,x_2}\sigma_{\x{m}y}'\sigma_{\x{f}x} & \sigma_{\x{f}x}^2\end{array}\right)\right)
\end{align*}


\begin{align*}
\frac{P_\x{f}(x_2,y_2)P_\x{m}(x_1,y_1)f_{y_2}(x_1)}{\int\int P_\x{m}(x_1,y_1)f_{y_2}(x_1)dx_1dy_1} &=\frac{1}{2\pi\sqrt{|\Sigma_\x{f}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\mu_\x{f})^T\Sigma_\x{f}^{-1}(\vec{x}_\x{f}-\mu_\x{f})\right)\frac{1}{2\pi\sqrt{|\bar{\Sigma}_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_m-\bar{\mu}_\x{m})^T\bar{\Sigma}_{\x{m}}^{-1}(\vec{x}_\x{m}-\bar{\mu}_\x{m})\right) 
\\ \Rightarrow \int\int P_\text{mate}(x_1,y_1,x_2,y_2)dx_1dx_2&=\frac{1}{\sqrt{2\pi\sigma_{\x{f}y}^2}}\exp\left(-\frac{(y_2-\mu_{\x{f}y})^2}{2\sigma_{\x{f}y}^2}\right)\frac{1}{\sqrt{2\pi\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}(1-\rho_\x{m})^2\right)\sigma_{\x{m}y}^2}}\exp\left(-\frac{\left(y_1-\mu_{\x{m}y}-\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}\frac{1}{\sigma^2+\sigma_{\x{m}x}^2}(y_2-\mu_{\x{m}x})\right)^2}{2\left(\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}(1-\rho_\x{m}^2)\right)\sigma_{\x{m}y}^2}\right)
\\&=\frac{1}{\sqrt{2\pi\sigma_{\x{f}y}^2}}\exp\left(-\frac{(y_2-\mu_{\x{f}y})^2}{2\sigma_{\x{f}y}^2}\right)\times
\\&\frac{1}{\sqrt{2\pi\left(1-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\rho_\x{m}^2\right)\sigma_{\x{m}y}^2}}\exp\left(-\frac{\left(y_1-\mu_{\x{m}y}-\frac{1}{\sigma_{\x{f}y}}\frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{f}y}}{\sqrt{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2}}\frac{\sigma_{\x{m}y}\sqrt{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2}}{\sigma^2+\sigma_{\x{m}x}^2}(y_2-\mu_{\x{m}x})\right)^2}{2\left(1-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\rho_\x{m}^2\right)\sigma_{\x{m}y}^2}\right)
\\\left(1-\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\rho_\x{m}^2\right)\sigma_{\x{m}y}^2&=(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+\sigma_{\x{m}x}^2-\rho_\x{m}^2\sigma_{\x{m}x}^2)\frac{\sigma_{\x{m}y}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2}
\\&=\frac{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2}\frac{\sigma_{\x{m}y}^2((\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}
\\&=\left(1-\frac{\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2}{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2}\right)\frac{\sigma_{\x{m}y}^2((\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2}
\\ \text{ If } \sigma_{\x{m}y}'^2&=\frac{\sigma_{\x{m}y}^2((\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2)}{(\sigma^2+\sigma_{\x{m}x}^2)^2} \text{ , } \sigma_{\x{f}y}'^2=\sigma_{\x{f}y}^2 \text{ , and } \rho_{y_1,y_2}  = \frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{f}y}}{\sqrt{(\sigma^2+\sigma_{\x{m}x}^2)(\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2\rho_\x{m}^2}} 
\\ \Rightarrow \int\int P_\text{mate}(x_1,y_1,x_2,y_2)dx_1dx_2&=\frac{1}{\sqrt{2\pi\sigma_{\x{f}y}^2}}\exp\left(-\frac{(y_2-\mu_{\x{f}y})^2}{2\sigma_{\x{f}y}^2}\right)\frac{1}{\sqrt{2\pi(1-\rho_{y_1,y_2}^2)\sigma_{\x{m}y}'^2}}\exp\left(-\frac{\left(y_1-\mu_{\x{m}y}-\frac{\rho_{y_1,y_2}\sigma_{\x{m}y}'}{\sigma_{\x{f}y}}(y_2-\mu_{\x{m}x})\right)^2}{2(1-\rho_{y_1,y_2}^2)\sigma_{\x{m}y}'^2}\right)
\\&=\frac{1}{\sqrt{2\pi\sigma_{\x{f}y}^2}}\exp\left(-\frac{(y_2-\mu_{\x{f}y})^2}{2\sigma_{\x{f}y}^2}\right)\frac{1}{\sqrt{2\pi(1-\rho_{y_1,y_2}^2)\sigma_{\x{m}y}'^2}}\exp\left(-\frac{\left(y_1-\mu_{\x{m}y}-\frac{\rho_{y_1,y_2}\sigma_{\x{m}y}'}{\sigma_{\x{f}y}}(\mu_{\x{f}y}-\mu_{\x{m}x})-\frac{\rho_{y_1,y_2}\sigma_{\x{m}y}'}{\sigma_{\x{f}y}}(y_2-\mu_{\x{f}y})\right)^2}{2(1-\rho_{y_1,y_2}^2)\sigma_{\x{m}y}'^2}\right)
\\&=\frac{1}{\sqrt{2\pi\sigma_{\x{f}y}^2}}\exp\left(-\frac{(y_2-\mu_{\x{f}y})^2}{2\sigma_{\x{f}y}^2}\right)\frac{1}{\sqrt{2\pi(1-\rho_{y_1,y_2}^2)\sigma_{\x{m}y}'^2}}\exp\left(-\frac{\left(y_1-\mu_{\x{m}y}-\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}(\mu_{\x{f}y}-\mu_{\x{m}x})-\frac{\rho_{y_1,y_2}\sigma_{\x{m}y}'}{\sigma_{\x{f}y}}(y_2-\mu_{\x{f}y})\right)^2}{2(1-\rho_{y_1,y_2}^2)\sigma_{\x{m}y}'^2}\right)
\\ \Rightarrow \int\int P_\text{mate}(x_1,y_1,x_2,y_2)dx_1dx_2& \sim N\left(\left(\begin{array}{cc} \mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}(\mu_{\x{f}y}-\mu_{\x{m}x}) \\ \mu_{\x{f}y}\end{array} \right),\left(\begin{array}{cc} \sigma_{\x{m}y}'^2 & \rho_{y_1,y_2} \sigma_{\x{m}y}'\sigma_{\x{f}y}' \\ \rho_{y_1,y_2} \sigma_{\x{m}y}'\sigma_{\x{f}y}' & \sigma_{\x{f}y}'^2 \end{array}\right)\right)
\end{align*}

\begin{align*}
P_\x{m}(x_1,y_1)f_{y_2}(x_1) & = \frac{1}{2\pi\sqrt{|{\Sigma}_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_m-{\mu}_\x{m})^T{\Sigma}_{\x{m}}^{-1}(\vec{x}_\x{m}-{\mu}_\x{m})\right)\frac{1}{\sqrt{2\pi\sigma^2}}\exp\left(-\frac{(y_2-x_2)^2}{2\sigma^2}\right)
\\ &=\frac{1}{2\pi\sqrt{|{\Sigma}_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_m-{\mu}_\x{m})^T{\Sigma}_{\x{m}}^{-1}(\vec{x}_\x{m}-{\mu}_\x{m})\right)\frac{1}{\sqrt{2\pi\sigma^2}}\exp\left(-\frac{1}{2}(\vec{x}_\x{m}-\nu)^TB^{-1}(\vec{x}_\x{m}-\nu)\right)
\\ \text{ where } \nu &= \left(\begin{array}{cc} y_2 \\ 0 \end{array} \right) \text{ and } B^{-1} = \left(\begin{array}{cc} \frac{1}{\sigma^2} & 0 \\ 0 & 0 \end{array}\right)
\\ (\vec{x}-\mu)^T\Sigma^{-1}(\vec{x}-\mu) + (\vec{x}-\nu)^TB^{-1}(\vec{x}-\nu)&=\vec{x}^T(\Sigma^{-1}+B^{-1})\vec{x}-2\vec{x}^T\Sigma^{-1}\mu  -2\vec{x}^TB^{-1}\nu +\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&=\vec{x}^T(\Sigma^{-1}+B^{-1})\vec{x}+-2\vec{x}^T(\Sigma^{-1}+B^{-1})(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&=\vec{x}^T(\Sigma^{-1}+B^{-1})\vec{x}-2\vec{x}^T(\Sigma^{-1}+B^{-1})(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}+B^{-1})(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)
\\&-(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&=(\vec{x}-(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu))^T(\Sigma^{-1}+B^{-1})(\vec{x}-(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu))
\\&-(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&=(\vec{x}-c)^TC^{-1}(\vec{x}-c)
\\&-(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&\text{ where } c = (\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu) \text{ and } C=(\Sigma^{-1}+B^{-1})^{-1}
\end{align*}
\begin{align*}
 |\Sigma|&=(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2\sigma_{\x{m}y}^2
\\ \Rightarrow \Sigma^{-1}&=\frac{1}{(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2\sigma_{\x{m}y}^2}\left(\begin{array}{cc}\sigma_{\x{m}y}^2 & -\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} \\ -\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} & \sigma_{\x{m}x}^2\end{array}\right)=\frac{1}{1-\rho_\x{m}^2}\left(\begin{array}{cc}\frac{1}{\sigma_{\x{m}x}^2} & -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)
\\ \Rightarrow  \Sigma^{-1}+B^{-1}&=\left(\begin{array}{cc}
\frac{1}{1-\rho_\x{m}^2}\frac{1}{\sigma_{\x{m}x}^2}+\frac{1}{\sigma^2} & -\frac{1}{1-\rho_\x{m}^2}\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ -\frac{1}{1-\rho_\x{m}^2}\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{1-\rho_\x{m}^2}\frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)=\frac{1}{1-\rho_\x{m}^2}\left(\begin{array}{cc}\frac{\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2}{\sigma^2\sigma_{\x{m}x}^2} & -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)
\\ \Rightarrow |\Sigma^{-1}+B^{-1}|&=\frac{1}{1-\rho_\x{m}^2}\frac{1}{\sigma_{\x{m}x}^2\sigma_{\x{m}y}^2}+\frac{1}{1-\rho_\x{m}^2}\frac{1}{\sigma^2}\frac{1}{\sigma_{\x{m}y}^2}=\frac{1}{1-\rho_\x{m}^2}\frac{1}{\sigma_{\x{m}y}^2}\left(\frac{\sigma^2+\sigma_{\x{m}x}^2}{\sigma^2\sigma_{\x{m}x}^2}\right)
\\ \Rightarrow (\Sigma^{-1}+B^{-1})^{-1}&=\frac{\sigma^2\sigma_{\x{m}x}^2\sigma_{\x{m}y}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\begin{array}{cc}\frac{1}{\sigma_{\x{m}y}^2} & \frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ \frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2}{\sigma^2\sigma_{\x{m}x}^2} \end{array}\right)=\left(\begin{array}{cc} \frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{m}x}^2 & \frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} \\ \frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} & \frac{\sigma^2+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{m}y}^2\end{array}\right)=\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\Sigma+\left(\begin{array}{cc}0 & 0 \\ 0 & \frac{(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{m}y}^2\end{array}\right)
\\ \text{Let } s & = \frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2} \text{ and } D  = \left(\begin{array}{cc}0 & 0 \\ 0 & \frac{(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{m}y}^2\end{array}\right) \text{ so } (\Sigma^{-1}+B^{-1})^{-1}=s\Sigma + D
\\ \Rightarrow -(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu&=-(\Sigma^{-1}\mu+B^{-1}\nu)(s\Sigma+D)(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&=-s\mu^T\Sigma^{-1}\mu-s\mu^T B^{-1}\nu-\mu^T\Sigma^{-1}D\Sigma^{-1}\mu-s\nu^TB^{-1}\mu-s\nu^TB^{-1}\Sigma B^{-1}\nu+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\ \Sigma^{-1}D\Sigma^{-1}&=\frac{1}{(1-\rho_\x{m}^2)^2}\left(\begin{array}{cc}\frac{1}{\sigma_{\x{m}x}^2} & -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)\left(\begin{array}{cc}0 & 0 \\ 0 & \frac{1-\rho_\x{m}^2}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{m}x}^2\sigma_{\x{m}y}^2\end{array}\right)\left(\begin{array}{cc}\frac{1}{\sigma_{\x{m}x}^2} & -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)
\\&=\frac{1}{(1-\rho_\x{m}^2)^2}\left(\begin{array}{cc}0 & -\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}\frac{1-\rho_\x{m}^2}{\sigma^2+\sigma_{\x{m}x}^2}\\ 0 & \sigma_{\x{m}x}^2\frac{1-\rho_\x{m}^2}{\sigma^2+\sigma_{\x{m}x}^2} \end{array}\right)\left(\begin{array}{cc}\frac{1}{\sigma_{\x{m}x}^2} & -\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} \\ -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)
\\&=\frac{1}{(1-\rho_\x{m}^2)^2}\left(\begin{array}{cc}\rho_\x{m}^2\frac{1-\rho_\x{m}^2}{\sigma^2+\sigma_{\x{m}x}^2} & -\frac{\rho_\x{m}\sigma_{\x{m}x}}{\sigma_{\x{m}y}}\frac{1-\rho_\x{m}^2}{\sigma^2+\sigma_{\x{m}x}^2} \\-\frac{\rho_\x{m}\sigma_{\x{m}x}}{\sigma_{\x{m}y}}\frac{1-\rho_\x{m}^2}{\sigma^2+\sigma_{\x{m}x}^2}& \frac{\sigma_{\x{m}x}^2}{\sigma_{\x{m}y}^2}\frac{1-\rho_\x{m}^2}{\sigma^2+\sigma_{\x{m}x}^2}  \end{array}\right)
\\ &=\frac{1}{1-\rho_\x{m}^2}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\begin{array}{cc}\frac{\rho_\x{m}^2}{\sigma_{\x{m}x}^2} & -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)
\\&=\frac{1}{1-\rho_\x{m}^2}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\begin{array}{cc}\frac{1}{\sigma_{\x{m}x}^2} & -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} \\ -\frac{\rho_\x{m}}{\sigma_{\x{m}x}\sigma_{\x{m}y}} & \frac{1}{\sigma_{\x{m}y}^2} \end{array}\right)+\frac{1}{1-\rho_\x{m}^2}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\left(\begin{array}{cc}\frac{\rho_\x{m}^2-1}{\sigma_{\x{m}x}^2} & 0 \\ 0 & 0 \end{array}\right)
\\ & = (1-s)\Sigma^{-1}-sB^{-1}
\\ \text{ and } sB^{-1}\Sigma B^{-1}&=s\left(\begin{array}{cc} \frac{1}{\sigma^2} & 0 \\ 0 & 0 \end{array}\right)\left(\begin{array}{cc} \sigma_{\x{m}x}^2 & \rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} \\ \rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} & \sigma_{\x{m}y}^2 \end{array}\right)\left(\begin{array}{cc} \frac{1}{\sigma^2} & 0 \\ 0 & 0 \end{array}\right)
\\&=s\left(\begin{array}{cc}\frac{1}{\sigma^2}\sigma_{\x{m}x}^2 & \frac{1}{\sigma^2}\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} \\ 0 & 0  \end{array}\right)\left(\begin{array}{cc} \frac{1}{\sigma^2} & 0 \\ 0 & 0 \end{array}\right)
\\&=s\left(\begin{array}{cc}\frac{1}{\sigma^4}\sigma_{\x{m}x}^2 & 0 \\ 0 &0  \end{array}\right)
\\ & = (1-s)B^{-1}
\\ \Rightarrow -(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu&=-s\mu^T\Sigma^{-1}\mu-s\mu^T B^{-1}\nu-\mu^T\left((1-s)\Sigma^{-1}-sB^{-1}\right)\mu-s\nu^TB^{-1}\mu-(1-s)\nu^TB^{-1}\nu+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&=s\mu^TB^{-1}\mu-2s\nu^TB^{-1}\mu+s\nu^TB^{-1}\nu
\\&=s(\nu-\mu)^TB^{-1}(\nu-\mu)
\end{align*}
\begin{align*}
\Rightarrow (\vec{x}-\mu)^T\Sigma^{-1}(\vec{x}-\mu) + (\vec{x}-\nu)^TB^{-1}(\vec{x}-\nu)&=(\vec{x}-c)^TC^{-1}(\vec{x}-c)+s(\nu-\mu)^TB^{-1}(\nu-\mu)
\\ \text{ where } C&=(\Sigma^{-1}+B^{-1})^{-1}=s\Sigma+D, \ c = C(\Sigma^{-1}\mu+B^{-1}\nu)
\\ \Rightarrow c &=(s\Sigma+D)(\Sigma^{-1}\mu+B^{-1}\nu)
\\&=s\mu+s\Sigma B^{-1}\nu+D\Sigma^{-1}\mu
\\&=s\mu+s\left(\begin{array}{cc}\frac{1}{\sigma^2}\sigma_{\x{m}x}^2 & 0 \\ \frac{1}{\sigma^2}\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y} & 0 \end{array}\right)\nu+(1-s)\left(\begin{array}{cc}0 & 0 \\ -\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}} & 1 \end{array}\right)\mu
\\&=\left(\begin{array}{cc}s\mu_{\x{m}x}+s\frac{1}{\sigma^2}\sigma_{\x{m}x}^2y_2 \\ s\mu_{\x{m}y}+s\frac{1}{\sigma^2}\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}y_2+(1-s)(-\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\mu_{\x{m}x}+\mu_{\x{m}y}) \end{array}\right)
\\&=\left(\begin{array}{cc}s\mu_{\x{m}x}+(1-s)y_2 \\ \mu_{\x{m}y}+s\frac{1}{\sigma^2}\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}y_2+(1-s)(-\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\mu_{\x{m}x}) \end{array}\right)
\\&=\left(\begin{array}{cc}s\mu_{\x{m}x}+(1-s)y_2 \\ \mu_{\x{m}y}+(1-s)\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}(y_2-\mu_{\x{m}x}) \end{array}\right)
\\ |C|&=|(\Sigma^{-1}+B^{-1})^{-1}|=|\Sigma^{-1}+B^{-1}|^{-1}
\\&=\frac{(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2\sigma_{\x{m}y}^2\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}=|\Sigma|\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}
\\ \Rightarrow P_\x{m}(x_1,y_1)f_{y_2}(x_1)&=\frac{1}{2\pi\sqrt{|\Sigma_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{m}-\mu_\x{m})^T\Sigma_\x{m}^{-1}(\vec{x}_\x{m}-\mu_\x{m})\right)\frac{1}{\sqrt{2\pi\sigma^2}}\exp\left(-\frac{(y_2-\mu_{\x{m}x})^2}{2\sigma^2}\right)
\\ &=\frac{1}{2\pi\sqrt{|\Sigma_\x{m}|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{m}-c)^TC^{-1}(\vec{x}_\x{m}-c)\right)\frac{1}{\sqrt{2\pi\sigma^2}}\exp\left(-\frac{(\mu_{\x{m}x}-y_2)^2}{2\frac{\sigma^2+\sigma_{\x{m}x}^2}{\sigma^2}\sigma^2}\right)
\\ &=\frac{1}{2\pi\sqrt{|\Sigma_\x{m}|\frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}}}\exp\left(-\frac{1}{2}(\vec{x}_\x{m}-c)^TC^{-1}(\vec{x}_\x{m}-c)\right)\frac{1}{\sqrt{2\pi(\sigma^2+\sigma_{\x{m}x}^2)}}\exp\left(-\frac{(\mu_{\x{m}x}-y_2)^2}{2(\sigma^2+\sigma_{\x{m}x}^2)}\right)
\\ &=\frac{1}{2\pi\sqrt{|C|}}\exp\left(-\frac{1}{2}(\vec{x}_\x{m}-c)^TC^{-1}(\vec{x}_\x{m}-c)\right)\frac{1}{\sqrt{2\pi(\sigma^2+\sigma_{\x{m}x}^2)}}\exp\left(-\frac{(\mu_{\x{m}x}-y_2)^2}{2(\sigma^2+\sigma_{\x{m}x}^2)}\right)
\end{align*}

\begin{align*}
\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\mu_\x{f})^T\Sigma_\x{f}^{-1}(\vec{x}_\x{f}-\mu_\x{f})\right)\exp\left(-\frac{\left(y_2-\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma_{\x{m}x}^2}}\right)&=\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\mu_\x{f})^T\Sigma_\x{f}^{-1}(\vec{x}_\x{f}-\mu_\x{f})\right)\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\nu)^TB^{-1}(\vec{x}_\x{f}-\nu)\right)
\\ \text{ where } \nu&=\left(\begin{array}{cc} 0 \\ \frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2} \end{array}\right) \text{ and } B^{-1}=\left(\begin{array}{cc} 0 & 0 \\ 0 & \frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)
\\ (\vec{x}-\mu)^T\Sigma^{-1}(\vec{x}-\mu) + (\vec{x}-\nu)^T B^{-1}(\vec{x}-\nu) &=(\vec{x}-c)^TC^{-1}(\vec{x}-c)-(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu + \nu^TB^{-1}\nu
\\ \text{ where } c&=(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu) \text{ and } C=(\Sigma^{-1}+B^{-1})^{-1}
\\ \Sigma^{-1}+B^{-1}&=\frac{1}{1-\rho_\x{f}^2}\left(\begin{array}{cc} \frac{1}{\sigma_{\x{f}x}^2} & -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} \\ -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} & \frac{1}{\sigma_{\x{f}y}^2}\end{array}\right) + \left(\begin{array}{cc} 0 & 0 \\ 0 & \frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)=\left(\begin{array}{cc}\frac{1}{1-\rho_\x{f}^2}\frac{1}{\sigma_{\x{f}x}^2} & -\frac{1}{1-\rho_\x{f}^2}\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}}\\ -\frac{1}{1-\rho_\x{f}^2}\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} & \frac{1}{1-\rho_\x{f}^2}\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma_{\x{f}y}^2\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)
\\ \Rightarrow |\Sigma^{-1}+B^{-1}| &=\frac{1}{1-\rho_\x{f}^2}\frac{1}{\sigma_{\x{f}x}^2}\frac{1}{\sigma_{\x{f}y}^2}+\frac{1}{1-\rho_\x{f}^2}\frac{\sigma_{\x{m}x}^2}{\sigma_{\x{f}x}^2\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}=\frac{1}{1-\rho_\x{f}^2}\frac{1}{\sigma_{\x{f}x}^2\sigma_{\x{f}y}^2}\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}
\\ \text{ Let } s&=\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2} \text{ and } D = \left(\begin{array}{cc} (1-\rho_\x{f}^2)(1-s)\sigma_{\x{f}x}^2 & 0 \\ 0 & 0 \end{array}\right)
\\ \Rightarrow C=(\Sigma^{-1}+B^{-1})^{-1} &= \left(\begin{array}{cc}\sigma_{\x{f}x}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{f}^2)\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2} & -\rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y}s \\ -\rho_{\x{f}}\sigma_{\x{f}x}\sigma_{\x{f}y}s & \sigma_{\x{f}y}^2s \end{array}\right)=s\Sigma + D
\\ \Rightarrow c & = (s\Sigma+D)(\Sigma^{-1}\mu+B^{-1}\nu)=s\mu+s\Sigma B^{-1}\nu+D\Sigma^{-1}\mu
\\&=s\mu+s\left(\begin{array}{cc}0 & \rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y}\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \\ 0 & \sigma_{\x{f}y}^2\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)\nu + \left(\begin{array}{cc}(1-s) & -\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}(1-s) \\ 0 & 0 \end{array}\right)\mu
\\&=\left(\begin{array}{cc}\mu_{\x{f}x}+\rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y}s\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}(1-s)\mu_{\x{f}y} \\ s\mu_{\x{f}y}+s\sigma_{\x{f}y}^2\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2} \end{array}\right)
\\&=\left(\begin{array}{cc}\mu_{\x{f}x}+\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}(1-s)\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}-\mu_{\x{f}y}\right)\\ s\mu_{\x{f}y}+(1-s)\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2} \end{array}\right)
\\-(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu + \nu^TB^{-1}\nu&=-(\Sigma^{-1}\mu+B^{-1}\nu)(s\Sigma+D)(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu + \nu^TB^{-1}\nu
\\&=-s\mu^T\Sigma^{-1}\mu-s\mu^TB^{-1}\nu-\mu^T\Sigma^{-1}D\Sigma^{-1}\mu-s\nu^TB^{-1}\mu-s\nu^TB^{-1}\Sigma B^{-1}\nu+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\end{align*}
\begin{align*}
\Sigma^{-1}D\Sigma^{-1}&=\frac{1}{(1-\rho_\x{f}^2)^2}\left(\begin{array}{cc} \frac{1}{\sigma_{\x{f}x}^2} & -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} \\ -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} & \frac{1}{\sigma_{\x{f}y}^2}\end{array}\right)\left(\begin{array}{cc} (1-\rho_\x{f}^2)(1-s)\sigma_{\x{f}x}^2 & 0 \\ 0 & 0 \end{array}\right)\left(\begin{array}{cc} \frac{1}{\sigma_{\x{f}x}^2} & -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} \\ -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} & \frac{1}{\sigma_{\x{f}y}^2}\end{array}\right)
\\&=\frac{1}{(1-\rho_\x{f}^2)^2}\left(\begin{array}{cc} (1-\rho_\x{f}^2)(1-s) & 0 \\ -\frac{\rho_\x{f}\sigma_{\x{f}x}}{\sigma_{\x{f}y}}(1-\rho_\x{f}^2)(1-s) & 0 \end{array}\right)\left(\begin{array}{cc} \frac{1}{\sigma_{\x{f}x}^2} & -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} \\ -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} & \frac{1}{\sigma_{\x{f}y}^2}\end{array}\right)
\\&=\frac{1-s}{1-\rho_\x{f}^2}\left(\begin{array}{cc} \frac{1}{\sigma_{\x{f}x}^2} & -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} \\ -\frac{\rho_\x{f}}{\sigma_{\x{f}x}\sigma_{\x{f}y}} & \frac{\rho_\x{f}^2}{\sigma_{\x{f}y}^2}\end{array}\right)
\\&=(1-s)\Sigma^{-1}-sB^{-1}
\\ sB^{-1}\Sigma B^{-1}&=s\left(\begin{array}{cc} 0 & 0 \\ 0 & \frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)\left(\begin{array}{cc}\sigma_{\x{f}x}^2 & \rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y} \\ \rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y} & \sigma_{\x{f}y}^2 \end{array}\right)\left(\begin{array}{cc} 0 & 0 \\ 0 & \frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)
\\&=s\left(\begin{array}{cc}0 & 0 \\ \rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y}\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} & \sigma_{\x{f}y}^2\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)\left(\begin{array}{cc} 0 & 0 \\ 0 & \frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)} \end{array}\right)
\\&=s\left(\begin{array}{cc} 0 & 0 \\ 0 & \sigma_{\x{f}y}^2\left(\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}\right)^2\end{array}\right)
\\&=\left(\begin{array}{cc} 0 & 0 \\ 0 & \frac{\sigma_{\x{f}y}\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}\sigma_{\x{f}y}}\frac{\sigma_{\x{m}x}}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}\end{array}\right)=(1-s)B^{-1}
\\ \Rightarrow -(\Sigma^{-1}\mu+B^{-1}\nu)(\Sigma^{-1}+B^{-1})^{-1}(\Sigma^{-1}\mu+B^{-1}\nu)+\mu^T\Sigma^{-1}\mu + \nu^TB^{-1}\nu&=-s\mu^T\Sigma^{-1}\mu-s\mu^TB^{-1}\nu-\mu^T\left((1-s)\Sigma^{-1}-sB^{-1}\right)\mu -s\nu^TB^{-1}\mu-(1-s)\nu^TB^{-1}\nu+\mu^T\Sigma^{-1}\mu+\nu^TB^{-1}\nu
\\&=s\nu^TB^{-1}\nu-2s\mu^TB^{-1}\nu+\mu^TsB^{-1}\mu
\\&=(\mu-\nu)^TsB^{-1}(\mu-\nu)
\\&=\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}\frac{\sigma_{\x{m}x}^2}{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}\left(\mu_{\x{f}y}-\frac{(\sigma^2+\sigma_{\x{m}x})^2x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)^2
\\&=\frac{\left(\mu_{\x{f}y}-\frac{(\sigma^2+\sigma_{\x{m}x})^2x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)^2}{\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}{\sigma_{\x{m}x}^2}}
\end{align*}
\begin{align*}
\Rightarrow \exp\left(-\frac{1}{2}(\vec{x}_\x{f}-\mu_\x{f})^T\Sigma_\x{f}^{-1}(\vec{x}_\x{f}-\mu_\x{f})\right)\exp\left(-\frac{\left(y_2-\left(\frac{(\sigma^2+\sigma_{\x{m}x}^2)x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)}{\sigma_{\x{m}x}^2}}\right)&=\exp\left(-\frac{1}{2}(\vec{x}_\x{f}-c)^TC^{-1}(\vec{x}_\x{f}-c)\right)\exp\left(-\frac{\left(\mu_{\x{f}y}-\frac{(\sigma^2+\sigma_{\x{m}x})^2x_1-\mu_{\x{m}x}\sigma^2}{\sigma_{\x{m}x}^2}\right)^2}{2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}{\sigma_{\x{m}x}^2}}\right)
\end{align*}
\newpage{}

SUMMARY of CORRELATIONS
{\tiny
\begin{align*}
P_\text{mate}(x_1,y_1,x_2,y_2)\sim N\left(\left(\begin{array}{cc} \frac{\sigma^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{m}x}+\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}\mu_{\x{f}y}
\\ \mu_{\x{m}y}+\frac{\rho_\x{m}\sigma_{\x{m}y}}{\sigma_{\x{m}x}}\frac{\sigma_{\x{m}x}^2}{\sigma^2+\sigma_{\x{m}x}^2}(\mu_{\x{f}y}-\mu_{\x{m}x})
\\ \mu_{\x{f}x}
\\ \mu_{\x{f}y}
\end{array}\right),
\Sigma'
\right)&
\\\text{ where } \Sigma' = \left(\begin{array}{cccc}\sigma_{\x{m}x}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2} & \frac{\rho_\x{m}\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma_{\x{m}x}\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sigma^2+\sigma_{\x{m}x}^2}\frac{\sigma_{\x{m}y} \sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sigma^2+\sigma_{\x{m}x}^2} &  \frac{\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma_{\x{m}x}\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{f}x} & \frac{\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma_{\x{m}x}\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{f}y}
\\ & \sigma_{\x{m}y}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2} & \frac{\rho_\x{m}\rho_\x{f}\sigma_{\x{f}y}\sigma_{\x{m}x}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma_{\x{m}y}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{f}x} & \frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{f}y}}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}\frac{\sigma_{\x{m}y}{\sqrt{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}}}{\sigma^2+\sigma_{\x{m}x}^2}\sigma_{\x{f}y}
\\ & & \sigma_{\x{f}x}^2 & \rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y}
\\ & & & \sigma_{\x{f}y}^2
\end{array}
\right)&
\end{align*}
}

\newpage{}

\begin{align*}
\Sigma'=\left(\begin{array}{cccc}\sigma_{\x{m}x}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2} & \frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}\left(\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2\right)}{(\sigma^2+\sigma_{\x{m}x}^2)^2} & \frac{\rho_{\x{f}}\sigma_{\x{m}x}^2\sigma_{\x{f}x}\sigma_{\x{f}y}}{\sigma^2+\sigma_{\x{m}x}^2} & \frac{\sigma_{\x{m}x}^2\sigma_{\x{f}y}^2}{\sigma^2+\sigma_{\x{m}x}^2} 
\\ & \sigma_{\x{m}y}^2\frac{\sigma^2(\sigma^2+\sigma_{\x{m}x}^2)+(1-\rho_\x{m}^2)\sigma_{\x{m}x}^2(\sigma^2+\sigma_{\x{m}x}^2)+\rho_\x{m}^2\sigma_{\x{f}y}^2\sigma_{\x{m}x}^2}{(\sigma^2+\sigma_{\x{m}x}^2)^2} & \frac{\rho_\x{m}\rho_\x{f}\sigma_{\x{m}x}\sigma_{\x{m}y}\sigma_{\x{f}x}\sigma_{\x{f}y}}{\sigma^2+\sigma_{\x{m}x}^2} & \frac{\rho_\x{m}\sigma_{\x{m}x}\sigma_{\x{m}y}\sigma_{\x{f}y}^2}{\sigma^2+\sigma_{\x{m}x}^2}
\\ & & \sigma_{\x{f}x}^2 & \rho_\x{f}\sigma_{\x{f}x}\sigma_{\x{f}y}
\\ & & & \sigma_{\x{f}y}^2
\end{array}\right)&
\end{align*}
{\footnotesize 
\begin{tabular}{|l|c|c|c|}
\hline  &  song from father &  song obliquely learned &  song genetic
\\ \hline  pref genetic & $\lim_{t\to\infty}\sigma_{y}^2=\lim_{t\to\infty}\sigma_{x}^2=0$ & $\lim_{t\to\infty}\sigma_{x}^2=\sigma_{x}(0)^2,\lim_{t\to\infty}\sigma_y^2=0$ & 
\\ \hline  pref imprinted from father & $\lim_{t\to\infty}\sigma_{y}^2=\lim_{t\to\infty}\sigma_{x}^2=0$ & $\lim_{t\to\infty}\sigma_{x}^2=\sigma_x^2(0),\lim_{t\to\infty}\sigma_y^2=\frac{\sigma_x^2(\sigma^2+\sigma_x^2)}{2\sigma_x^2+\sigma^2}$ & 
\\ \hline  pref learned from mother / obliquely & $\lim_{t\to\infty}\sigma_y^2=\sigma_y^2(0),\lim_{t\to\infty}\sigma_{x}^2=\sigma_y^2-\sigma^2$ & $\lim_{t\to\infty}\sigma_y^2=\sigma_y^2(0),\lim_{t\to\infty}\sigma_x^2=\sigma_x^2(0)$ & 
\\ \hline 
\end{tabular}
}
\section{Equilibrium for various modes of inheritance }
\subsection{Song from father, pref genetic}
\begin{align*}
\sigma_{x}(t+1)^2&=\sigma_{x}^2\frac{\sigma^2(\sigma^2+\sigma_{x}^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}
\\ \sigma_y(t+1)^2&=\frac{1}{4}\sigma_y^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+(1-\rho^2)\sigma_x^2(\sigma^2+\sigma_x^2)+\rho^2\sigma_x^2\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+\frac{1}{2}\frac{\rho\sigma_x\sigma_y^3}{\sigma^2+\sigma_x^2}+\frac{1}{4}\sigma_y^2 
\\ &=\frac{\sigma_y^2}{4}\left(\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+(1-\rho^2)\sigma_x^2\frac{\sigma^2+\sigma_x^2-\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+\frac{2\rho\sigma_x\sigma_y}{\sigma^2+\sigma_x^2}+1\right)
\\ \Cov_{x,y}(t+1)&=\frac{1}{2}\frac{\rho\sigma_x\sigma_y\left(\sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2\sigma_y^2\right)}{(\sigma^2+\sigma_x^2)^2}+\frac{1}{2}\frac{\sigma_x^2\sigma_y^2}{\sigma^2+\sigma_x^2}
\\\text{ equilibrium } \Rightarrow \sigma^2+\sigma_x^2=\sigma_y^2 \Rightarrow \sigma_x<\sigma_y
\\ \Rightarrow \sigma_y(t+1)^2&=\frac{\sigma_y^2}{4}\left(1+\frac{2\rho\sigma_x}{\sigma_y}+1\right)
\\ \Rightarrow \sigma_y(t+1)^2&<\sigma_y(t)^2
\\ \Rightarrow \lim_{t\to\infty}\sigma_x(t)^2=\lim_{t\to\infty}\sigma_y(t)^2=0
\end{align*}

\begin{align*}
\text{If $\sigma^2=0$, } \sigma_x(t+1)^2&=\sigma_y^2
\\ \sigma_y(t+1)^2&=\frac{\sigma_y^2}{4}\left(\frac{\sigma_y^2}{\sigma_x^2}+(1-\rho^2)\frac{\sigma_x^2-\sigma_y^2}{\sigma_x^2}+\frac{2\rho\sigma_y}{\sigma_x}+1\right)
\\\Cov(t+1)&=\frac{1}{2}\frac{\rho\sigma_x\sigma_y\sigma_y^2}{\sigma_x^2}+\frac{1}{2}\sigma_y^2
\\ \text{ equilibrium } \Rightarrow \sigma_x^2&=\sigma_y^2
\\ \Rightarrow 2+2\rho&=4
\\ \Rightarrow \rho&=1
\\ \text{YOU'RE HERE!!!}
\end{align*}
\subsection{Song learned from father, pref imprinted from father} 
\begin{align*}
\sigma_x(t+1)^2&=\sigma_x^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2} 
\\ \sigma_y(t+1)^2&=\sigma_x^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}
\end{align*}
Cannot happen that both $\sigma_x^2=\sigma_y^2-\sigma^2$ and $\sigma_y^2=\sigma_x^2$ unless $\sigma^2=0$, in which case $\lim_{t\to\infty}\sigma_x(t)^2=\lim_{t\to\infty}\sigma_y(t)^2=\sigma_y(0)^2$.
\subsection{Song learned from father, pref learned from mother}
\begin{align*}
\sigma_x(t+1)^2&=\sigma_x^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}
\\ \sigma_x(t+1)^2&=\sigma_x^2 \Rightarrow \sigma^2+\sigma_x^2=\sigma_y^2
\end{align*}
\subsection{Song learned obliquely, pref genetic }
\begin{align*}
\sigma_x(t+1)^2&=\sigma_x^2
\\ \sigma_y(t+1)^2&=\frac{1}{4}\sigma_y^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+(1-\rho^2)\sigma_x^2(\sigma^2+\sigma_x^2)+\rho^2\sigma_x^2\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+\frac{1}{2}\frac{\rho\sigma_x\sigma_y^3}{\sigma^2+\sigma_x^2}+\frac{1}{4}\sigma_y^2 
\\&=\frac{1}{4}\sigma_y^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2(\sigma^2+\sigma_x^2)}{(\sigma^2+\sigma_x^2)^2}+\frac{1}{4}\sigma_y^2  \text{ since in this case $\rho=0$}
\\&=\frac{1}{2}\sigma_y^2
\\ \Rightarrow \lim_{t\to\infty}\sigma_y(t)^2&=0
\end{align*}
\subsection{Song learned obliquely, pref imprinted from father}
\begin{align*}
\sigma_x(t+1)^2&=\sigma_x^2
\\ \sigma_y(t+1)^2&= \sigma_x^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}
\\ \sigma_y(t+1)^2&\geq\sigma_y^2 \Rightarrow \sigma_x^2(\sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2\sigma_y^2)\geq\sigma_y^2(\sigma^2+\sigma_x^2)^2
\\ \Rightarrow \left(\sigma^4+2\sigma^2\sigma_x^2+\sigma_x^4-\sigma_x^4\right)\sigma_y^2&\leq\sigma_x^2\sigma^2(\sigma^2+\sigma_x^2)
\\ \Rightarrow \sigma^2(\sigma^2+2\sigma_x^2)\sigma_y^2&\leq\sigma^2\sigma_x^2(\sigma^2+\sigma_x^2)
\\ \Rightarrow \sigma_y^2&\leq\frac{\sigma_x^2(\sigma^2+\sigma_x^2)}{\sigma^2+2\sigma_x^2} 
\end{align*}
Stable equilibrium with $\sigma_x^2=\sigma_x(0)^2$ and $\sigma_y^2=\frac{\sigma_x^2(\sigma^2+\sigma_x^2)}{2\sigma_x^2+\sigma^2}$.
\subsection{Song obliquely, pref obliquely }
Neither distribution changes.
\subsection{Song genetic, pref genetic } 
\begin{align*}
\sigma_x(t+1)^2&=\frac{1}{4}\sigma_x^2\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}+\frac{1}{2}\frac{\rho\sigma_x^3\sigma_y}{\sigma^2+\sigma_x^2}+\frac{1}{4}\sigma_x^2
\\&=\frac{\sigma_x^2}{4}\left(\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}+\frac{2\rho\sigma_x\sigma_y}{\sigma^2+\sigma_x^2}+1\right)
\\\sigma_y(t+1)^2&=\frac{1}{4}\sigma_y^2\left(\frac{\sigma^2(\sigma^2+\sigma_x^2)+(1-\rho^2)\sigma_x^2(\sigma^2+\sigma_x^2)+\rho^2\sigma_x^2\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+\frac{2\rho\sigma_x\sigma_y}{\sigma^2+\sigma_x^2}+1\right)
\\&=\frac{1}{4}\sigma_y^2\left(\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+\frac{2\rho\sigma_x\sigma_y}{\sigma^2+\sigma_x^2}+1\right)+\frac{1-\rho^2}{4}\frac{\sigma_x^2\sigma_y^2(\sigma^2+\sigma_x^2-\sigma_y^2)}{(\sigma^2+\sigma_x^2)^2}
\\ \Cov(t+1)&=\frac{1}{4}\left(\rho\sigma_x\sigma_y\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+\frac{\sigma_x^2\sigma_y^2}{\sigma^2+\sigma_x^2}+\frac{\rho^2\sigma_x^2\sigma_y^2}{\sigma^2+\sigma_x^2}+\rho\sigma_x\sigma_y\right)
\\&=\frac{\Cov(t)}{4}\left(\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2\sigma_y^2}{(\sigma^2+\sigma_x^2)^2}+\frac{2\rho\sigma_x\sigma_y}{\sigma^2+\sigma_x^2}+1\right)+\frac{1-\rho^2}{4}\frac{\sigma_x^2\sigma_y^2}{\sigma^2+\sigma_x^2}
\end{align*}
\begin{align*}
\text{ Let } Q&=\frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}+\frac{2\rho\sigma_x\sigma_y}{\sigma^2+\sigma_x^2}+1
\\ \Rightarrow \sigma_x(t+1)^2&=\frac{Q}{4}\sigma_x^2
\\ \sigma_y(t+1)^2&=\frac{Q}{4}\sigma_y^2+\frac{1-\rho^2}{4}\frac{\sigma_x^2\sigma_y^2(\sigma^2+\sigma_x^2-\sigma_y^2)}{(\sigma^2+\sigma_x^2)^2}
\\ \Cov(t+1)&=\frac{Q}{4}\Cov(t) +\frac{1-\rho^2}{4}\frac{\sigma_x^2\sigma_y^2}{\sigma^2+\sigma_x^2}
\\\text{ equilibrium } \Rightarrow Q & = 4 
\\ \Rightarrow \frac{1-\rho^2}{4}\frac{\sigma_x^2\sigma_y^2}{\sigma^2+\sigma_x^2} & = 0
\\ \Rightarrow \rho&=1 \text{ or }  \sigma_x^2=0 \text{ or } \sigma_y^2=0
\\ \sigma_x^2&=0 \Rightarrow Q = 2 \text{ and } \sigma_y^2=0 \Rightarrow Q = \frac{\sigma^2}{\sigma^2+\sigma_x^2}+1\leq 2
\\ \text{ so at equilibrium need both } \sigma_x^2&=0,\sigma_y^2=0 
\\ \text{ or } \sigma_x^2&>0,\sigma_y^2>0, \text{ and } \rho=1
\\ Q = 4 \Rightarrow \frac{\sigma^2(\sigma^2+\sigma_x^2)+\sigma_y^2\sigma_x^2}{(\sigma^2+\sigma_x^2)^2}+\frac{2\rho\sigma_x\sigma_y}{\sigma^2+\sigma_x^2} & = 3
\\ \Rightarrow \sigma^2(\sigma^2+\sigma_x^2)+\sigma_x^2\sigma_y^2+2\rho\sigma_x\sigma_y(\sigma^2+\sigma_x^2) & = 3(\sigma^2+\sigma_x^2)^2
\\ \Rightarrow 
\end{align*}
\end{landscape} 




This model was built to study whether song diversity can be maintained when two populations come back together. However, even within one population there are interesting dynamics.
\begin{enumerate}
\item There can be many discrete ``popular" songs when $\sigma_\text{m}^2$  is small, $\sigma_\text{f}^2$ is high, and $\sigma^2$ is intermediate.
\item When the equilibrium population is unimodal, there is an interesting interaction between $\sigma^2$ and $\sigma_\text{f}^2$: At low $\sigma^2$ and low $\sigma_\text{f}^2$, the males are even more narrowly distributed than the females because the male trait preferred by the most females does way better than anyone else. At low $\sigma^2$ and high $\sigma_\text{f}^2$, the male distribution matches the female distribution. At high $\sigma^2$, $\sigma_\text{f}^2$ does not matter and the male distribution is moderately narrow because average males can mate with most females. 
\end{enumerate}

\bibliographystyle{plainnat}
\bibliography{song_learning_evolution}


\end{document}
